Universal Anonymous Signatures

### 2022-04-11 prism-backend/research/gsac/model-uas.tex
Refined UAS model. Seems ok, but need to add extractability definition.

In the following, we assume a setting with multiple groups. For simplicity,
we assume that each has its own issuer and inspector.

\todo{Are generalizations where different groups can share issuer or inspector
  straight forward?}

@@

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. Hereafter, we assume that the
  public part \ipk is added to the group public key \gpk, as well as \fissue.
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers). Hereafter, we assume that the
  public part \opk is added to the group public key \gpk, along with \finsp.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
  \rangle$.] %
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
  where $\cred_i$ is a credential obtained from the issuer with public
  key $\ipk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\ipk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$\sig \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
  The user with with secret key \usk, owner of credentials $\cred_i$, signs
  \msg, so that the inspector with public key \opk may open it if needed.
  Evaluation function \feval is used to produce the signature.
\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
  \msg,\feval)$.] Checks whether \sig is a valid signature over message \msg,
  from a user in the group with credentials issued by issuers with public keys
  $\ipk_i$, for evaluation function \feval and inspector key \opk.
\item[$(\y,\iproof)/\bot \gets \Inspect(\osk,\lbrace \ipk_i
  \rbrace_{i \in \Issuers},\sig,\msg,\feval)$.] %
  \todo{I think we do not need \trans here, see the generic construction. (This
    was somehow inherited from \cite{bsz05}.) However, if it is indeed not
    needed, it is noteworthy that we include/need it in \GSAC, but not here.
    Justify/understand better why!}
  Executed by the inspector with private key \osk. Receives a signature \sig
  over message \msg and evaluation function \feval. If \sig is valid, the
  function outputs a value $\y$ derived from the signer's public key,
  credentials, message, and signature, as well as a proof of correct
  inspection.
\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\y,\iproof,
  \sig,\msg,\feval)$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \y,
  obtained by applying \Inspect to the the signature \sig over message \msg,
  and for evaluation function \feval. 
\end{description}

The correctness and security properties are defined with the help of the
following sets of oracles, and global variables that help oracles and games
keep consistent state.

@@

\begin{description}
\item[$\fissue: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\attrs)
  \rightarrow 0/1$.] Defined by issuers for the credentials they grant,
  governs what customized conditions an issuer requires in order to issue
  credentials, when receiving a request from user with public key \upk, for
  attributes \attrs. \fissue may run checks on a (possibly empty) set of
  additional credentials $\cred_i$, all bound to \upk, and possibly issued
  by other issuers. \fissue returns $1$ to accept a request, $0$ to reject it.  
\item[$\feval: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\msg)
  \rightarrow \varrngfeval$.] Can be defined by
  any party, although we anticipate that this will typically be done by either
  signers, verifiers, or some governance organization. It defines customized
  conditions to be met by the owner of a user key \upk and credentials $\cred_i$,
  bound to \upk, in order to sign a concrete message \msg. Its outputs
  $\varrngfeval$ must belong in a well defined set \rngfeval, with the
  restriction that it must return $0$ when the conditions for signing are not
  met.
\item[$\finsp: (\varrngfeval,\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
  \msg) \rightarrow \varrngfinsp$.]
  Chosen by inspectors. It defines what utility value, derived from the user's
  public key, credentials, and message, should be extractable by an inspector.
  Note that \finsp also receives as input a value in the range of the \feval
  function, \rngfeval. This will allow inspection logic to depend on the value
  produced by the evaluation function. The output of \finsp is a value
  \varrngfinsp, which must belong in a well defined set \rngfinsp.
\end{description}

@@

\paragraph{Helper Function \Identify.} In addition, we make use of a helper
function \Identify for some of our definitions. This function receives
a signature and a user secret key, and determines whether the latter was used
to produce the former. This is in line with previous works on DAA
\cite{bfg+11,cdl16} and group signatures without traditional open functions
\cite{dl21,fgl21,gl19}. More concretely, the \Identify function, defined as $1/0
\gets \Identify(\usk,\sig)$, conveys meaning to our definitions conditioned on
the fact that, given a signature \sig accepted by \Verify, \Identify returns $1$
for exactly one \usk.

@@

\begin{description}
\item[Tables for parties]:
  \begin{description}
  \item[\HU and \CU.] Keep track of honest (\HU) and corrupted (\CU) users;
    i.e., they are sets of {\uid}s.
  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers.
    Since we assume only one issuer per group, they are sets of {\gid}s.
  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) inspectors.
    Since we assume only one inspector per group, they are sets of {\gid}s.
  \end{description}
\item[Tables for keys]:
  \begin{description}
  \item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$.
    To refer to the key pair of a specific user, we use $\UK[\uid]$. \PUBUK
    is a shorthand to refer to the public part, and \PRVUK refers to the
    private part -- we may also index both by \uid.
  \item[\IK, \PUBIK and \PRVIK.] Same as \UK, but for issuer key pairs. In
    addition, \IK also includes the \fissue function, which is part of the
    public key.
  \item[\OK, \PUBOK, \PRVOK.] Same as \UK, but for inspector key pairs. In
    addition, \OK also includes the \finsp function, which is part of the
    public key.
  \end{description}
\item[Tables for credentials-related data]:
  \begin{description}
  \item[\CRED.] Stores information related to credentials obtained by honest
    users. Thus, it is indexable by \cid. More specifically, it stores tuples of
    the form $(\uid,\cred,\gid,\attrs,\scid)$, where \uid is the identity of the
    owner of the credential, \cred (when available) is the credential itself,
    \gid is the identifier of the group to which the credential belongs, \attrs
    are the attributes included in \cred, and \scid are the identifiers of any
    additional credential that \uid used to request \cred.
  \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
    ``\uid such that $\CRED[\cid] = (\uid, \cdot, \cdot, \cdot, \cdot)$''.
  \item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
    ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
  \item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
    ``\iid such that $\CRED[\cid] = (\cdot, \iid, \cdot, \cdot, \cdot)$''.
  \end{description}
\item[Tables for signatures]:
  \begin{description}
  \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
    of honest users.
  \item[\CSIG.] Maintains challenge signatures, generated via the \CHALb oracle,
    by one of the challenge users in the anonymity game.
  \end{description}
\end{description}

@@

        \procedure{$\IGEN(\iid,\fissue)$}{%
          \pcif \iid \in \HI \lor \iid \in \CI: \pcreturn \bot \\
          (\ipk,\isk) \gets \IKeyGen(\parm) \\
          \IK[\iid] \gets ((\ipk,\fissue),\isk) \\
          \HI \gets \HI \cup \lbrace \iid \rbrace \\
          \pcreturn \ipk \\
        }

@@

        \procedure{$\OGEN(\oid,\finsp)$}{%
          \pcif \oid \in \HO \lor \oid \in \CO: \pcreturn \bot \\
          (\opk,\osk) \gets \OKeyGen(\parm) \\
          \OK[\oid] \gets ((\opk,\finsp),\osk) \\
          \HO \gets \HO \cup \lbrace \oid \rbrace \\
          \pcreturn \opk \\
        }

@@

        \procedure{$\CHALb(\oid,\cscid_{0,1},\msg,\feval)$}{%
          \pcif \pcfor d \in \bin~\exists \ccid_d,{\ccid}'_d \in \cscid_d~\st \\
          \pcind \OWNR[\ccid_d] \neq \OWNR[{\ccid}'_d]: \\
          \pcind \pcreturn \bot \\
          \cuid_0 \gets \OWNR[\cscid_0]; \cuid_1 \gets \OWNR[\cscid_1] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \oid \in \CO: \pcreturn \bot \\
          % \pcif \feval(\PUBUK[\cuid_0],\CRED[\cscid_0],\msg) \neq \\
          % \pcind \feval(\PUBUK[\cuid_1],\CRED[\cscid_1],\msg):
          % \pcreturn \bot \\
          \csig_b \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid],\CRED[\cscid_b],
          \msg,\feval) \\
          \csig_{1-b} \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid],
          \CRED[\cscid_{1-b}],\msg,\feval) \\          
          \CSIG[\csig_b] \gets 
          \lbrace (\csig_{1-b},\msg,\feval) \rbrace \\
          \pcreturn \csig_b
        }

@@

        \procedure{$\SIGN(\oid,\scid,\msg,\feval)$}{%
          \pcif \exists \cid,\cid' \in \scid~\st~\OWNR[\cid] \neq \OWNR[\cid']:
          \pcreturn \bot \\
          \uid \gets \OWNR[\scid] \\
          \pcif \uid \notin \HU \lor
          \exists \cid \in \scid~\st~\CRED[\cid] = \bot: \pcreturn \bot \\
          \sig \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,\feval) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\sig,\msg,\feval) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\INSPECT(\oid,\sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\sig,\msg,\feval)
          \in \SIG[\uid] \\
          (\y,\iproof) \gets
          \Inspect(\PRVOK[\oid],\GK[\scid],\sig,\msg,\feval) \\
          \pcif \CSIG[\sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\sig_{1-b},\msg,\feval)$} \\
          \pcind (\y_{1-b},\iproof_{1-b}) \gets
          \Inspect(\PRVOK[\oid],\IK[\siid],\\
          \hspace*{107pt} \sig_{1-b},\msg,\feval) \\
          \pcind \pcif \y_{1-b} \neq \y: \pcreturn \bot \\
          \pcreturn (\y,\iproof)
        }

@@

\paragraph{Correctness.} %
Correctness of \UAS schemes is formalized through the experiment in
\figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
and valid function \feval \todo{Should we explicitly check \feval in the game?
  If so, how?},
produced honestly by an honest user \uid with credential \cid, is accepted by
\Verify. Moreover, upon issuance of the credential \cid, it must have met the
conditions set by \fissue. Similarly, the value returnd by \Inspect must be
accepted by \Judge, and must match the output of applying \finsp on \feval, the
credential, user key, and message.

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\oid,\scid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
    \sig \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = 0: \pcreturn 1~
    \pccomment{\sig fails to verify} \\
    \pcif \CorrectIssue(\uid,\scid) = 0: \pcreturn 1~
    \pccomment{Some \cid should not have been issued} \\
    % \pcif \CorrectEval(\uid,\cid,\msg,\feval)
    % = 0: \pcreturn 1~
    % \pccomment{\msg should not have been signed} \\
    \pcif \CorrectEvalInspect(\oid,\uid,\scid,\msg,\sig,\feval) = 0: \pcreturn 1~
    \pccomment{The combination of evaluation and inspection is wrong} \\
    \pcreturn 0 \\
  }

@@

  % \procedure{$\CorrectEval(\uid,\cid,\msg,\feval)$}{
  %   \pcif \feval(\PUBUK[\uid],\CRED[\cid],\msg) = 0: \pcreturn 0 \\
  %   \pcreturn 1 \\
  % }

  \procedure{$\CorrectEvalInspect(\oid,\uid,\scid,\msg,\sig,\feval)$}{
    \textrm{Parse}~\OK[\oid]~\textrm{as}~((\cdot,\finsp^\gid),\cdot) \\
    \pccomment{\sig cannot be inspected} \\
    \pcif \Inspect(\PRVOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = \bot:
    \pcreturn 0 \\
    \pccomment{The produced $(\y,\iproof)$ pair is rejected by \Judge
      % \todo{This must be conditioned on \feval = 0!}
    } \\
    \pcif (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\PUBIK[\scid],\sig,
    \msg,\feval) \land
    \Judge(\PUBOK[\oid],\PUBIK[\scid],\y,\iproof,\sig,\msg,\feval) = 0: \\
    \pcind \pcreturn 0 \\
    \pccomment{\y is the wrong value} \\
    \pcif \y \neq \finsp^\gid(\feval(\PUBUK[\uid],\CRED[\scid],\msg),
    \PUBUK[\uid],\CRED[\scid],\msg)):
    \pcreturn 0 \\
    \pcreturn 1
  }

@@

In our notion of anonymity for \UAS, we need to merge the previous constraints.
Furthermore, a key difference with group signatures is that the game requires
the adversary to output credential identifiers, rather than user identifiers.
Specifically, this means that the adversary may actually output two credentials
that belong to the same user. Therefore, in some sense, the anonymity we get is
more general than that of group signatures. Moreover, in order to prevent
trivial wins by the adversary, we have to restrict that the challenge signatures
belong to a group that has been ``programmed'' with the same evaluation and
inspection functions, which is again a generalization over group signatures,
as discussed in the sequel. Other than this, the overall approach is the same:
the adversary picks two honestly obtained credentials, and one of them (set
by the $b$ value defining the $anon-b$ game) is used to program the \CHALb
oracle. The formal specification of the anonymity game is
given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,\CU\rbrace
\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,
\INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace
\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\INSPECT,\CHALb)$

\begin{figure}[htp!]
  \procedure{$\ExpAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\cscid_0,\cscid_1,\status) \gets \adv^{\Oanonc}(\choose,\parm) \\
     b^* \gets \adv^{\Oanong} (\guess,\status) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure}

>>>>

An \UAS scheme is composed by the following algorithms.

@@

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers).
\item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
  where $\cred_i$ is a credential obtained from the issuer with public
  key $\ipk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\ipk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
  Upon receiving a user secret key \usk, inspector public key \opk, a set of
  credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
  function \feval, returns signature \sig and value \yeval.
\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
  \yeval,\msg,\feval)$.] Checks whether $(\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys $\ipk_i$, for evaluation function \feval and inspector key \opk.
\item[$(\yinsp,\iproof)/\bot \gets \Inspect(\osk,\lbrace \ipk_i
  \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
  \todo{I think we do not need \trans here, see the generic construction. (This
    was somehow inherited from \cite{bsz05}.) However, if it is indeed not
    needed, it is noteworthy that we include/need it in \GSAC, but not here.
    Justify/understand better why!}
  Executed by the inspector with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
  the function outputs a value $\yinsp$ derived from the signer's public key,
  credentials, message, and signature, as well as a proof of correct
  inspection.
\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
  \iproof,\sig,\yeval,\msg,\feval)$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \yinsp,
  obtained by applying \Inspect to the the signature $(\sig,\yeval)$ over
  message \msg, and for evaluation function \feval. 
\end{description}

@@

\begin{description}
\item[$\fissue: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\attrs)
  \rightarrow 0/1$.] Chosen by issuers within a family of functions \famfissue,
  the issuance function defines what customized conditions an issuer requires
  in order to issue credentials, when receiving a request from user with public
  key \upk, for attributes \attrs. \fissue may run checks on a (possibly empty)
  set of additional credentials $\cred_i$, all bound to \upk, and possibly
  issued by other issuers. \fissue returns $1$ to accept a request, $0$ to
  reject it.
\item[$\feval: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\msg)
  \rightarrow \yeval$.] Evaluation functions, from a family of functions
  \famfeval, can be set on a per-signature basis. The evaluation function
  defines customized conditions to be met by the owner of a user key \upk and
  credentials $\cred_i$, bound to \upk, in order to sign a concrete message
  \msg. Its outputs \yeval must belong in a well defined set \rngfeval.
\item[$\finsp: (\yeval,\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
  \msg) \rightarrow \yinsp$.]
  Chosen by inspectors from a family of functions \famfinsp. The inspection
  functions define what utility value, derived from the user's public key,
  credentials, and signed message, should be extractable by an inspector.
  Note that \finsp also receives as input a value in the range of the \feval
  function, \rngfeval. This will allow inspection logic to depend on the value
  produced by the evaluation function. The output of \finsp is a value
  \yinsp, which must belong in a well defined set \rngfinsp.
\end{description}

@@

\paragraph{Helper Function \Identify.} %
\todo{We use extract now...} In addition, we make use of a helper
function \Identify for some of our definitions. This function receives
a signature and a user secret key, and determines whether the latter was used
to produce the former. This is in line with previous works on DAA
\cite{bfg+11,cdl16} and group signatures without traditional open functions
\cite{dl21,fgl21,gl19}. More concretely, the \Identify function, defined as $1/0
\gets \Identify(\usk,\sig)$, conveys meaning to our definitions conditioned on
the fact that, given a signature \sig accepted by \Verify, \Identify returns $1$
for exactly one \usk.

@@

\begin{description}
\item[Tables for parties]:
  \begin{description}
  \item[\HU and \CU.] Keep track of honest (\HU) and corrupted (\CU) users;
    i.e., they are sets of {\uid}s.
  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers;
    i.e., they are sets of {\iid}s.
  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) inspectors;
    i.e., they are sets of {\oid}s.
  \end{description}
\item[Tables for keys]:
  \begin{description}
  \item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
    user, we use $\UK[\uid]$. 
  \item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
    $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
    use \PUBIK to refer to the public component, which also includes the \fissue
    function; and \PRVIK refers to the private component of the key pair.
  \item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for inspector key pairs. Instead
    of \fissue, \OK includes the \finsp function.
  \end{description}
\item[Tables for credentials-related data]:
  \begin{description}
  \item[\CRED.] Stores information related to credentials obtained by honest
    users. Thus, it is indexable by \cid. More specifically, it stores tuples of
    the form $(\uid,\cred,\iid,\attrs,\scid)$, where \uid is the identity of the
    owner of the credential, \cred (when available) is the credential itself,
    \iid is the identifier of the credential issuer, \attrs are the attributes
    included in \cred, and \scid are the identifiers of the credentials (if any)
    that \uid used to request \cred.
  \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
    ``\uid such that $\CRED[\cid] = (\uid, \cdot, \cdot, \cdot, \cdot)$''.
  \item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
    ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
  \item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
    ``\iid such that $\CRED[\cid] = (\cdot, \iid, \cdot, \cdot, \cdot)$''.
  \end{description}
\item[Tables for signatures]:
  \begin{description}
  \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
    of honest users. Entries of this table are $(\oid,\scid,\sig,\yeval,\msg,
    \feval)$,
    where \oid is the inspector chosen for the signature, \scid is the set of
    credentials used for signing, \feval is the evaluation function, and \sig
    and \msg are the produced signature and signed message.
  \item[\CSIG.] Maintains challenge signatures output to the adversary; i.e.,
    the table is indexable by challenge signatures \csig.
    Each entry contains also $\cuid_b$ and $\scid_b$ the challenge user and
    credential identifiers set used to produce \csig; as well as the
    corresponding challenge user and credential set indexed by the complementary
    $1-b$; the signed message \msg and evaluation function \feval, the result of
    \feval, \yeval, and the inspector identifier \oid.
  \end{description}
\end{description}

@@

        \procedure{$\IGEN(\iid,\fissue)$}{%
          \pcif \iid \in \HI \lor \iid \in \CI: \pcreturn \bot \\
          \pcif \fissue \notin \famfissue: \pcreturn \bot \\
          (\ipk,\isk) \gets \IKeyGen(\parm) \\
          \IK[\iid] \gets ((\ipk,\fissue),\isk) \\
          \HI \gets \HI \cup \lbrace \iid \rbrace \\
          \pcreturn \ipk \\
        }

@@

        \procedure{$\OGEN(\oid,\finsp)$}{%
          \pcif \oid \in \HO \lor \oid \in \CO: \pcreturn \bot \\
          \pcif \finsp \notin \famfinsp: \pcreturn \bot \\
          (\opk,\osk) \gets \OKeyGen(\parm) \\
          \OK[\oid] \gets ((\opk,\finsp),\osk) \\
          \HO \gets \HO \cup \lbrace \oid \rbrace \\
          \pcreturn \opk \\
        }

@@

        \procedure{$\CHALb(\oid,\cuid_{0,1},\cscid_{0,1},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \oid \in \CO: \pcreturn \bot \\
          \pcif \yeval = \feval(\PUBUK[\cuid_0],\CRED[\cscid_0],\msg) \neq \\
          \pcind \feval(\PUBUK[\cuid_1],\CRED[\cscid_1],\msg):
          \pcreturn \bot \\
          (\yeval,\csig_b) \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
          (\yeval,\csig_{1-b}) \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
          \CSIG[\csig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\msg,\feval,\yeval,\\
          \hspace*{74pt}\cuid_{1-b},\csig_{1-b},\cscid_{1-b})
          \rbrace \\
          \pcreturn \csig_b
        }

@@

        \procedure{$\SIGN(\oid,\uid,\scid,\msg,\feval)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          (\sig,\yeval) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,
          \feval) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\sig,\yeval,\msg,\feval) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\INSPECT(\oid,\sig,\yeval,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\sig,\yeval,\msg,\feval)
          \in \SIG[\uid] \\
          (\yinsp,\iproof) \gets
          \Inspect(\PRVOK[\oid],\GK[\scid],\sig,\yeval,\msg,\feval) \\
          \pcif \CSIG[\sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
            \feval,\yeval$} \\
          \hspace*{83pt}\cuid_{1-b},\csig_{1-b},\scid_{1-b}) \\
          \pcind (\yinsp',\iproof') \gets
          \Inspect(\PRVOK[\oid],\IK[\siid],\\
          \hspace*{107pt} \sig_{1-b},\msg,\feval) \\
          \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
          \pcreturn (\yinsp,\iproof)
        }

@@

\paragraph{Correctness.} %
Correctness of \UAS schemes is formalized through the experiment in
\figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
and valid function \feval produced honestly leveraging credential set \scid,
owned by user \uid, is accepted by \Verify. Moreover, all the credentials in
\scid met the conditions set by the corresponding \fissue defined by the issuer
which issued each credential. Similarly, the output \yeval of \feval matches the
value produced by \Sign alognside with \sig; and the value produced by \Inspect
is accepted by \Judge, and matches the output of applying \finsp on \yeval, the
credentials, user key, and message.

\begin{definition}{(Correctness of \UAS)}
  An \UAS scheme is correct if, for any p.p.t. adversary $\adv$, \ExpCorrect
   outputs 1 with negligible probability.
\end{definition}

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\oid,\scid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
    \pcif \feval \notin \famfeval: \pcreturn 0 \\
    \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
    (\sig,\yeval) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = 0: \pcreturn 1~
    \pccomment{\sig fails to verify} \\
    \pcif \CorrectIssue(\uid,\scid) = 0: \pcreturn 1~
    \pccomment{Some \cid should not have been issued} \\
    \pcif \CorrectEval(\oid,\uid,\scid,\msg,\sig,\yeval,\feval) = 0: \pcreturn 1~
    \pccomment{The result of evaluation is wrong} \\
    \pcif \CorrectInspect(\oid,\uid,\scid,\msg,\sig,\yeval,\feval) = 0: \pcreturn 1~
    \pccomment{The result of inspection is wrong} \\
    \pcreturn 0 \\
  }

@@

  \procedure{$\CorrectEval(\oid,\uid,\scid,\msg,\sig,\yeval,\feval)$}{%
    \pcif \feval(\UK[\uid],\CRED[\scid],\msg) \neq \yeval: \pcreturn 0 \\
    \pcreturn 1 \\
  }

  \procedure{$\CorrectInspect(\oid,\uid,\scid,\msg,\sig,\yeval,\feval)$}{
    \textrm{Parse}~\OK[\oid]~\textrm{as}~((\cdot,\finsp^\gid),\cdot) \\
    \pccomment{\sig cannot be inspected} \\
    \pcif \Inspect(\PRVOK[\oid],\PUBIK[\scid],\sig,\yeval,\msg,\feval) = \bot:
    \pcreturn 0 \\
    \pccomment{The produced $(\y,\iproof)$ pair is rejected by \Judge} \\
    \pcif (\yinsp,\iproof) \gets \Inspect(\PRVOK[\gid],\PUBIK[\scid],\sig,
    \msg,\feval)~\land \\
    \hspace*{10pt}
    \Judge(\PUBOK[\oid],\PUBIK[\scid],\y,\iproof,\sig,\yeval,\msg,\feval) = 0: \\
    \pcind \pcreturn 0 \\
    \pccomment{\yinsp is the wrong value} \\
    \pcif \yinsp \neq \finsp^\gid(\yeval,\UK[\uid],\CRED[\scid],\msg)):
    \pcreturn 0 \\
    \pcreturn 1
  }

@@

In our notion of anonymity for \UAS, we need to merge the previous constraints.
In order to prevent trivial wins by the adversary, we have to restrict that the
evaluation function outputs the same value for both user-credentials pairs. Very
interestingly, since our inspection functionality does not (necessarily) output
the identity of the signer, \uline{we can even allow the adversary to
  inspect challenge signatures, as long as they produce the same output upon
  inspection}. Other than this, the overall approach is similar: as in group
signatures and anonymous credentials, the adversary picks two pairs of honest
users and credential sets. We also require the adversary to pick an evaluation
function and an inspector (hence, an inspection function). Then, the
user-credential pair defind by the value of $b$ (unknown to the adversary) is
used to program the \CHALb oracle. The formal specification of the anonymity
game is given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,
\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,
\WREG,\SIGN,\INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,
\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\INSPECT,\CHALb)$
